\textbf{ \Large {Decentralized autonomous sensor fault detection using neural networks}}

### 2015-02-12 Paper/PaperJahrSchlich.tex
blaue Änderungsmarkierungen hinzugefügt

\begin{figure}[htb]
    \centering
    \includegraphics{figures/dataflow_tasks.eps}
    \caption{Dataflow and associated SHM tasks}
    \label{fig:flow}
\end{figure}

The SHM system is programmed object-oriented in Java. 
Object orientation uses objects, which are instanciated using classes as paradigm. 
A class includes methods, allowing the objects to perform actions, and attributes, storing object-specific data.
The SHM system consists of two packages---\texttt{sensornode} and \texttt{basestation}.
A package organizes several Java classes that build a program.

\autoref{fig:UML-sn} describes the classes of the \texttt{sensor\-node} package.
The package \texttt{sensor\-node} consists of the classes \texttt{Acceleration\-Sampler}, \texttt{FFT}, \texttt{Communi\-cation} and \texttt{Main\-Spot}, which are embedded directly into the sensor nodes.
The \texttt{Acceleration\-Sampler} class is responsible for measuring the acceleration.
There are two phases: At first, the acceleration is measured with a low sampling rate.
Once the acceleration exceeds a threshold, the second phase is entered by increasing the sampling rate. 
The measured values are stored into an array.
The different phases are indicatad by lighting different LEDs.
The \texttt{FFT} class performs a FFT on the measured accelerations. 
With the transformed data, the magnitudes and the correlating frequencies of the measured oscillation are calculated.
Finally, the natural frequency is determined by extracting the maximal magnitude.
The \texttt{Communi\-cation} class opens a radio connection between the sensor node and the basestation to transfer data from the sensor node to the basestation.
For starting the operation of the sensor node, the entry point of the programm is the \texttt{start\-App()} method in the \texttt{Main\-Spot} class. 
Within the \texttt{Main\-Spot} class, instances of the \texttt{Acceleration\-Sampler} class, the \texttt{FFT} class and the \texttt{Communication} class are created to perform the measurement.

@@

Every sensor calculated the same natural frequency to a precision of four decimal points regardless of sensor position and degree of excitation.
Example results are shown in \autoref{tab:lab-ex}.
The identified magnitudes increase with ascending sensor node position from top to bottom, corresponding to the higher deflection at the top of the structure.

Through FFT analysis of sampling events, the data traffic is decreased from 512 doubles per sampling event to two doubles per sampling event.
A number stored in the used data format double occupies 8\,bytes of space.
The data traffic is decreased by (512$-$2)$\times$8\,B\,=\,4080\,B\,=\,3,98\,MB per sampling event, decreasing data traffic by 99.6\,\%.

>>>>

\begin{figure}[htb]
    \centering
    \includegraphics{figures/dataflow_tasks_nn.eps}
    \caption{Dataflow and associated SHM tasks}
    \label{fig:flow}
\end{figure}

\colorbox{cyan}{neuer Absatz:}
The SHM system is programmed object-oriented in Java. 
Object orientation uses objects, which are instanciated using classes as paradigm. 
A class includes methods, allowing the objects to perform actions, and attributes, storing object-specific data.
The SHM system consists of two packages---\texttt{sensornode} and \texttt{basestation}.
A package organizes several Java classes that build a program.

\autoref{fig:UML-sn} describes the classes of the \texttt{sensor\-node} package.
The package \texttt{sensor\-node} consists of the classes \texttt{Acceleration\-Sampler}, \texttt{FFT}, \texttt{Communi\-cation} and \texttt{Main\-Spot}, which are embedded directly into the sensor nodes.
The \texttt{Acceleration\-Sampler} class is responsible for measuring the acceleration.
There are two phases: \colorbox{cyan}{At} first, the acceleration is measured with a low sampling rate.
Once the acceleration exceeds a threshold, the \colorbox{cyan}{second phase is entered} by increasing the sampling rate. 
The measured values are stored into an array.
The different phases are indicatad by lighting different LEDs.
The \texttt{FFT} class performs a FFT on the measured accelerations. 
With the transformed data, the magnitudes and the correlating frequencies of the measured oscillation are calculated.
Finally, the natural frequency \colorbox{cyan}{is} determined by extracting the maximal magnitude.
The \texttt{Communi\-cation} class opens a radio connection between the sensor node and the basestation to transfer data from the sensor node to the basestation.
For starting the operation of \colorbox{cyan}{the sensor node}, the entry point of the programm is the \texttt{start\-App()} method in the \texttt{Main\-Spot} class. 
Within the \texttt{Main\-Spot} class, instances of the \texttt{Acceleration\-Sampler} class, the \texttt{FFT} class and the \texttt{Communication} class are created to perform the measurement.

@@

\textit{Every sensor calculated the same natural frequency to a precision of four decimal points regardless of sensor position and degree of excitation.
Example results are shown in \autoref{tab:lab-ex}.
The identified magnitudes increase with ascending sensor node position from top to bottom, corresponding to the higher deflection at the top of the structure.}

\textit{Through FFT analysis of sampling events, the data traffic is decreased from 512 doubles per sampling event to two doubles per sampling event.
A number stored in the used data format double occupies 8\,bytes of space.
The data traffic is decreased by (512$-$2)$\times$8\,B\,=\,4080\,B\,=\,3,98\,MB per sampling event, decreasing data traffic by 99.6\,\%.}
